Study on the effectiveness of the investment strategy based on a classifier with rules adapted by machine learning

### 2013-12-12 Article/Article20130912/LatexArt/tewi-paper-template_minipages.tex
Intorduction poprawione

An investment strategy with a relatively high complexity (measured by the number of factors included in the model), derived from a strategies group called strategy of simple rules (simple rules) was built. In the literature those strategies are considered to be mainly strategies based on moving averages - their intersections and derivatives shown for example by Brock et al. \cite{Brock}, Cai et al. \cite{Cai} and many other authors \cite{Gencay, LeBaron, Tian}. Of course, the world of algorithms as well as prediction methods using a completely different nature, such as regression \cite{Muriel}, multiple regression \cite{Wilinski, Fujimoto}, Fourier and wavelet transforms, and many others \cite{Raghuraj, KleskWilinski} is plenteous. This methods are used as a basis for comparison, however the main focus is on mentioned simple rules.\\

This paper proposes strategy, that differs by suggesting different behaviors than the ones proposed when using Bollinger's Band, which has its foundation in a band built in an unusual way. According to the strategy based on that band, generally it can be assumed that the trend is horizontal and it is recommended to open position to the center of the band, after its cross by the price from the inside. In proposed strategies, another band that is based on maxima of the maxima and minima of the minima of last several candles is used.\\

In considered strategies authors move away from the principle of opening positions to the center of the band. In one modification, hereinafter referred to as sub strategy, position opens into the center of the band, whereas in another one, position opens on the outside. By treating the two considered sub strategies as an entirety and as strategies that are mutually retrieving (although a more appropriate word would be complementary) it is assumed, that in the selected trading section, opening positions in opposite directions, of course not at the same time, can be done intentionally and effectively. During the trading, nature of the market (trend, volatility) may change. The market may be in some periods horizontal, in other trended. It is appropriate to seek all opportunities for profit. A similar philosophy is applied by several Krutsinger correspondents \cite{Krutsinger}, who belong to most prominent traders in USA, who advocate unfounded reversal of the direction of opening the positions in case of series of failures.\\

Returning to the issue of the complexity of the strategy, there are often opinions that the growing complexity of the prediction model is not indicated, because in learning section it  leads to overfitting \cite{Murphy, Cai, Fujimoto}  resulting in a greater error in the test sections. The problem of selecting the proper ratio between learning and testing phase is still unsolved for the non-stationary time series \cite{Ball, Ivakhnenko}. In this situation the right approach seems to be the use of the idea of computational intelligence \cite{Polya, Pedrycz} by which the empirical justification hypothesis entitles to use the model.\\

>>>>

An investment strategy with a relatively high complexity (measured by the number of factors included in the model) was built, derived from a strategies group called strategy of simple rules (simple rules). In the literature those strategies are considered to be mainly strategies based on moving averages - their intersections and derivatives shown for example by Brock et al. \cite{Brock}, Cai et al. \cite{Cai} and many other authors \cite{Gencay, LeBaron, Tian}. Of course, the world of algorithms as well as prediction methods is using a completely different nature, such as regression \cite{Muriel}, multiple regression \cite{Wilinski, Fujimoto}, Fourier and wavelet transforms, and many others \cite{Raghuraj, KleskWilinski} is plenteous. This methods are used as a basis for comparison, however the main focus is on mentioned simple rules.\\

This paper proposes strategy, which differs by suggesting different behaviors than the ones proposed when using Bollinger's Band, which has its foundation in a band built in an unusual way. According to the strategy based on that band, generally it can be assumed that the trend is horizontal and it is recommended to open position to the center of the band, after its cross by the price from the inside. In proposed strategies, another band that is based on maxima of the maxima and minima of the minima of last several candles is used.\\

Considered strategies move away from the principle of opening positions to the center of the band. In one modification, hereinafter referred to as sub strategy, position opens into the center of the band, whereas in another one, position opens on the outside. By treating the two considered sub strategies as an entirety and as strategies that are mutually retrieving (although a more appropriate word would be complementary) it is assumed, that in the selected trading section, opening positions in opposite directions, of course not at the same time, can be done intentionally and effectively. During the trading, nature of the market (trend, volatility) may change. The market may be in some periods horizontal, in other trended. It is appropriate to seek all opportunities for profit. A similar philosophy is applied by several Krutsinger correspondents \cite{Krutsinger}, who belong to most prominent traders in USA, who advocate unfounded reversal of the direction of opening the positions in case of series of failures.\\

Returning to the issue of complexity of strategy, there are often opinions that the growing complexity of the prediction model is not indicated, because in learning section it  leads to overfitting \cite{Murphy, Cai, Fujimoto}  resulting in a greater error in the test sections. The problem of selecting the proper ratio between learning and testing phase is still unsolved for the non-stationary time series \cite{Ball, Ivakhnenko}. In this situation the right approach seems to be the use of the idea of computational intelligence \cite{Polya, Pedrycz} by which the empirical justification hypothesis entitles to use the model.\\
